% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
  \item[]%
  }
  {\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
  }
  {\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
  \end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}
% and the actual content starts here
\begin{document}

\begin{center}
  {\LARGE \textbf{Leo Przybylski}}

  \ \ 2450 N. Palo Hacha\ \ \textbullet
  \ \ Tucson, AZ 85745
  \\
  (520) 440-1252\ \ \textbullet
  \ \ r351574nc3 @ gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Objective}
To obtain a position with a reliable, well-established
company/institution as highly-ranked development manager or software
architect.

\subsection*{Summary of Qualifications}
16 years experience including n-tier enterprise application development with Java, software 
documentation with UML, and working with unified/agile processes. 
\begin{itemize}
\item Developed software using Ruby, Python, Groovy, and Perl scripting languages.
\item Strong agile/kanban/iconix development process experience.
\item Generated source code of XML, SQL, and interpreted scripting languages.
\item Developed software using SOA and template-driven UI with Oracle and MySQL.
\item Strong experience with Struts, Spring MVC, RoR, Django, Play Framework, and Grails.
\item Experience with Rich and Simple domain models with OR/M.
\item NOSQL database experience with databases like Berkeley DB, BigTable, Redis, and CouchDB.
\item Enthusiasm and motivation to work with new technologies.
\item Experienced with Web Components and Polymer/Xtags.
\item Proven experience with javascript web frameworks like EmberJS and AngularJS.
\item Proven experience in rich user interfaces with javascript libraries jQuery, Dojo, 
  prototype, and scriptaculous.
\item Aware of tools useful in varying applications, and actively
  searches for better solutions to improve work output and productivity.
\item Proven experience in rich user interfaces with AJAX.
\item Capable of writing/maintaining technical documentation and
  specifications with LaTeX, UML/ER diagrams, flowcharts, Atlassian Confluence or Microsoft Word.
\item Strong familiarity with SCM tools RPM, Jenkins, Ant, Ivy, Maven 3, SVN and Git.
\item Strong familiarity with metadata standards and ontologies
  including RDF, Dublin Core, FOAF, Microformats, OWL, DAML, and OAI.
\item Some experience in VB 5.0 from 1997 - 1998.
\end{itemize}

\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em

\item
  \headerrow
  {\textbf{KualiCo}}
  {\textbf{Scottsdale, AZ}}
  \\
  \headerrow
  {\emph{SaaS Developer}}
  {\emph{October 2014 -- November 2014}}
  \begin{itemize*}
    \item Developed features and improvements for Kuali Coeus and Kuali Rice.
  \end{itemize*}

\item
  \headerrow
  {\textbf{rSmart}}
  {\textbf{Scottsdale, AZ}}
  \\
  \headerrow
  {\emph{SaaS Developer}}
  {\emph{May 2014 -- October 2014}}
  \begin{itemize*}
    \item I provided assistance and technical guidance directly to the Vice President of Product Development for rSmart Cloud Express.
    \item I created online training courseware for rSmart Rice/KRAD training.
    \item I provided training on Kuali Rice and KRAD to institution staff members.
    \item I simplified data migration by developing custom kuali liquibase extensions that allowed a simple for YAML/XML formats for business analysts to use.
    \item I simplified testing of data migration scripts and tools by developing custom Maven plugins.
    \item I developed Maven archetypes for KFS, Kuali Coeus, and Kuali Rice platforms to simplify institutions starting new projects.
    \item I also developed features and improvments for Kuali Coeus and Kuali Rice platforms.
    \item I worked in DevOps by maintaining tools using Chef, Puppet, Hiera, AWS tools, Ruby, Elasticsearch, Docker, and Java.
    \item I also developed custom data migration tools using ReST, Ruby, Spring Framework, and Jersey.
    \item I managed open source projects maintained on GitHub including pull requests and code reviews.
    \item To improve continuous delivery and adapt software to be more favorable to multitenant applications, I ported a metadata architecture to NoSQL Redis datastore.
    \item To automate integration tests that require a running Redis server, I developed a Redis Maven Plugin.
    \item I integrated Gerrit Code review into Kuali Enterprise Workflow in order to manage real-time modifications to a live application with a workflow.
  \end{itemize*}
  \headerrow
  {\emph{Kuali Student Team Lead (Kuali Foundation)}}
  {\emph{April 2013 -- December 2013}}
  \begin{itemize*}
  \item Estimated and planned two phases for porting a GWT project to Kuali Foundation KRAD.
  \item Developed features, fixes, and tests for porting a GWT project to KRAD.
  \item Collaborated with and led a development team dispersed in different continents.
  \item Provided technical and managerial leadership to developers.
  \end{itemize*}

  \headerrow
  {\emph{Kuali Developer III}}
  {\emph{2012 -- May 2014}}
  \begin{itemize*}
  \item Traveled to higher education institutions and help them to develop customizations to KFS, KC, and Kuali Rice source code.
  \item Developed test plans and strategies for automated unit tests, usability tests, and integration. 
  \item Advised on performance, performance testing, security, and software configuration management. 
  \item Responsible for providing training materials and execution of training staff at higher education institutions on large
    scale software systems, web services, middleware, and java web application development. 
  \item Collaborated with a dispersed development team including subject matter experts and business analysts on the Travel and Entertainment Module. 
  \item Responsible for determining development process, technical design and writing of technical specifications, software development, and change management. 
  \item Mentored other developers at rSmart.
  \item Worked in DevOps by configuring multitier applications with Tomcat, Apache HTTPD, OpenLdap, MySQL, and CAS/Shibboleth.
  \end{itemize*}

  \headerrow
  {\emph{Release Manager (Kuali Foundation)}}
  {\emph{2011 -- 2012}}
  \begin{itemize*}
  \item I developed tools to manage the Kuali Rice software
    release process. 
  \item I also worked on releasing software to the sonatype nexus
    repository for the Kuali Foundation. This led to releases
    regularly becoming available via maven central for the
    org.kuali groupId. 
  \item I simplified our EC2 deployment process by including
    automated delivery of software, automated Jenkins Slave nodes,
    and automated AMI and Volume/Snapshot backups for EC2. We were
    a small team and my focus was largely to reduce the
    responsibility for developers through automation so they could
    focus more on development and less on process. 
  \item I also worked with the development team by configuring
    and handling the performance analysis of Kuali Rice. By
    configuring tools like java visualvm, java melody, jprobe,
    hprof, the java garbage collector, jrocket JVM, and yourkit,
    I have contributed in helping improve performance in Kuali
    applications. 
  \item I have also learned and experienced much in areas such
    as performance tuning the JVM.
  \item Developed a recommended reference implementation continuous
    integration/deployment setup using vagrant and puppet
    provisioning for Universities to quickly get started with their
    Kuali Foundation software implementations.
  \end{itemize*}
  
  \headerrow
  {\emph{Java Developer, Senior}}
  {\emph{2010 -- 2011}}
  \begin{itemize*}
  \item Collaborated with a dispersed development team
    including subject matter experts and business analysts on the
    Travel and Entertainment Module. 
  \item Responsible for determining development process, technical design and writing of technical
    specifications, software development, and change management.
  \item I also am a mentor to other developers at rSmart.
  \item Created training materials for Kuali Coeus, Kuali
    Fiancials, Kuali Rice, Liquibase, and LDAP.
  \item Developed a virtual machine with vagrant that is provisioned
    via Puppet to create training development environments for
    trainees to quickly become emmersed within the development tools.
  \end{itemize*}

\item
  \headerrow
  {\textbf{ClearBox Media, Inc.}}
  {\textbf{Tucson, AZ}}
  
  \headerrow
  {\emph{Development Manager}}
  {\emph{May 2012 -- December 2012}}
  \begin{itemize*}
  \item Responsible for determining technologies we use at Clearbox
    Media and the technical direction of our company. 
  \item Developed location-based social, event tracking system built
    on a graph API and a graph database.
  \item Developed a SOA system for federating events from
    EventBrite, Eventful, and Facebook into an event tracking
    system.
  \item Integrated elasticsearch indexing into our event federating
    system.
  \item Migrated an application built around Document-based NoSQL
    database (CouchDb) to a graph based database system (Neo4j)
  \end{itemize*}
  
\item
  \headerrow
  {\textbf{University of Arizona }}
  {\textbf{Tucson, AZ}}
  
  \headerrow
  {\emph{Mosaic/KFS Architect / Mosaic Project Implementation}}
  {\emph{October 2008 -- September 2010}}
  \begin{itemize*}
  \item I managed and designed integration efforts between
    external systems like Peoplesoft and Kuali applications. 
  \item I also created and maintained the development process used
    for kuali applications developers to
    produce/maintain/disseminate documentation. 
  \item Occassionally, I define scope, developed project plans,
    give time estimates and monitored progress of implementation
    assignments to project team members. 
  \item I coordinated ongoing operational research, evaluate results and recommend selections of emerging and/or relevant methodologies, programming languages and technologies. 
  \item I have coordinated with training professionals to provide
    training for developers, users, and administrators of the UA
    Kuali implementation. 
  \item I have also coordinated and documented status, setup details, process information, and
    policies between implementation and environment teams. 
  \item Designed a plan for change promotion process for emergency changes, bug fixes, and software updates.
  \item Collaborated with the software development team and system/network administrators to improve the implementation architecture for reliability and sustainability.
  \item Personally handled staffing and training of configuration management personnel.
  \item Designed architecture for concurrent continuous integration and configuration management of systems across KFS and KC implementations.
  \item Designed systems management and development dashboards to provide diagnostic views of KFC and KC implementations.
  \item Integrated KFS with UA Enterprise Directory Service and BMC Control-M.
  \end{itemize*}

  \headerrow
  {\emph{Kuali Research Administration Senior Developer}}
  {\emph{July 2007 -- September 2008}}
  \begin{itemize*}
  \item Developed new software components for the Proposal Development module
  \item Created materials and taught sessions at several Kuali Bootcamp training events
  \end{itemize*}

  \headerrow
  {\emph{Kuali Financial System Labor Distribution Development Manager and Team Lead}}
  {\emph{November 2006 -- July 2007}}
  \begin{itemize*}
  \item Manage tasks/issues for resources using Atlassian Jira.
  \item Create Confluence documentation templates for Labor Distribution developer documentation.
  \item Participated team-oriented design and development of new software components based on an existing system.
  \item Created gap-analysis between two existing software system to estimate project length and resources.
  \item Trained and coached new project developers on tools (Spring, Struts MVC, OJB, and proprietary project technologies.)
  \item Collaborated with Subject Matter Experts (SMEs) to develop timelines, functional and technical specifications, test plans, and usability test coordination.
  \item Created Labor Distribution status reports used to inform the Kuali Foundation Board of Directors about project progress.
  \item Developed new software components for the Labor Distribution module of
    the Kuali Financial System using Spring, DWR, Struts MVC, OJB, Kuali
    Rice, Kuali Nervous System, Kuali Enterprise Worfkflow, and JSP/JSTL.
  \end{itemize*}

  \headerrow
  {\emph{Application Systems Analyst, Senior}}
  {\emph{June 2005 -- November 2006}}
  \begin{itemize*}
  \item Collaborated with Subject Matter Experts (SMEs) to better
    understand Financial Information Systems (FIS,) an existing software
    system used by higher education institutions, and functional
    requirements of the new software system.
  \item Maintenance development work for Kuali Project (an enterprise financial system for higher education.)
  \item Created presentations and proposals for new refactoring using
    Atlassian Confluence, LaTeX, and UML technologies.
  \item Developed and maintained written documention of developed components using Atlassian Confluence
  \item Built OJB Mappings and Data Access Objects for persistent storage Business Objects.
  \item Developed Services in a SOA software system to be integrated with Spring Framework.
  \item Participated in design of new frameworks such as unit testing frameworks designed for specific components of the software project and a business rules validation framework.
  \item Participated in design and development of source code generating
    engines for generating OJB mappings, POJO's for business objects,
    proprietary framework XML descriptors, and unit test datasets.
  \end{itemize*}

\item
  \headerrow
  {\textbf{IBM}}
  {\textbf{Tucson, AZ}}
  \\
  \headerrow
  {\emph{Software Engineer}}
  {\emph{April 2004 -- June 2005}}
  \begin{itemize*}
  \item Performing maintenance design, development, and documentation for WebSM user interface the NAS 500.
  \item Developing NAS 500 extensions to AIX WebSM using Java, KORN/BASH shell scripting, Perl scripting, and Sed/Awk scripting.
  \item Maintaining hardware and server software configuration of test and development servers in NAS test lab.
  \item Assisting test personnel in configuring and executing test scenarios by debugging hardware and software problems as well as efficient use of workarounds.
  \item Supported Enterprise Storage Server and FastT server integration with NAS 500.
  \item Providing support as a resource to other team members for network site and software configuration (i.e. configuring network bridges, configuring network for HAGEO/HACMP configuration, and troubleshooting network configuration issues.)
  \item Providing support as a resource to other team members for shell scripting and java software development.
  \item Developed user interface, error inject, and test automation tools for functional verification test of IBM total storage systems (Reef and Megamouth Shark) using BASH shell scripting, Perl, and C/C++ (GTK+).
  \item Assisted in hardware support and maintenance of IBM total storage
    systems (Reef) by troubleshooting and replacing various hardware
    components.
  \end{itemize*}

\item
  \headerrow
  {\textbf{University of Arizona}}
  {\textbf{Tucson, AZ}}
  \\
  \headerrow
  {\emph{Application Systems Analyst}}
  {\emph{January 2002 -- April 2004}}
  \begin{itemize*}
  \item Mentored student developers
  \item Created development environment suitable for multiple developers/programmers to collaborate easily on projects significantly reducing development time. Included systems for code concurrency, a build environment and tools to integrate with IDE's.
  \item Researched and analyzed complex software systems for integration with GROW systems.
  \item Created testing unit environment/framework with code concurrency 
    demographics/statistics to enhance quality assurance of products.
  \item Coordinated with administrative and technical personnel concerning implementation and adaptation of complex operating systems and related software to meet users needs.
  \item Created tools and processes for project management to manage collaborative team projects.
  \item Developed/designed two-tier, long-term and low maintenance application system architecture for a digital library based-on metadata structure, collection, and transport using standards/protocols such as Dublin Core and Open Archives Initiative Protocol for Metadata Harvesting.
  \item Developed/designed metadata binding API for binding metadata in XML/Java Objects/Database Structure.
  \item Developed/designed metadata browsing/directory service for browsing metadata from a repository through a directory service API (JNDI).
  \item Designed database structure to support storage flexible to support different metadata formats (Dublin Core, GROW, etc...) in mass quantities on MySQL and Oracle DBMS.
  \item Managed MySQL DBMS migration to Oracle DBMS.
  \end{itemize*}

\item
  \headerrow
  {\textbf{Coremetrics, Inc.}}
  {\textbf{Austin, TX}}
  \\
  \headerrow
  {\emph{Network Systems Programmer/Analysis, and Data
      Acquisition Engineer}}
  {\emph{June 1999 -- November 2001}}
  \begin{itemize*}
  \item Developed three-tier distributed applications with Java using Servlets, JSP, JDBC 2.0 (oracle Platform), Enterprise Java Beans 1.1 JINI 1.0.1 and Java Spaces.
  \item Maintained Apache Web Server module used for data collection.
  \item Developed network tools to validate links and Cormetrics JavaScript code on remote E-Commerce sites.
  \item Developed tools using Perl, Java, C/C++ and BASH to simulate multitudes of concurrent client connections to servers and load-balancing hardware/software over protocols such as SSL, SSH, RSH, HTTP, and JMS.
  \item Developed tools written in various languages (Perl, BASH, PHP) for validating integrity of data frequently transported across network domains of database servers.
  \item Developed tools for encrypted data transport over TCP/IP using C/C++ and Java.
  \item Engineered Enterprise solution using Java, XML, and/or C/C++ for database analysis and network communication between servers, domains and subnets by message protocols over multicast or point-to-point networking standards.
  \item Increased data security and integrity in Cormetrics network
    communication architecture with tools that handle software
    load-balancing, dynamic network data transfer demographics, multiple
    future plans for standard data structures with XML, XSLT, XML-schemas,
    and proprietary encoding formats.
  \end{itemize*}

\item
  \headerrow
  {\textbf{The Automation Centre}}
  {\textbf{Tucson, AZ}}
  \\
  \headerrow
  {\emph{Lotus Domino Database Developer}}
  {\emph{1997 - 1998}}
  \begin{itemize*}
  \item Developed Lotus Notes and Lotus Domino Applications with VB 5.0 and VBScript.
  \end{itemize*}
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

\item 
  \headerrow
  {\textbf{Pima County Community College}}
  {\textbf{Tucson, AZ}}
  \\
  \headerrow
  {\emph{AGECS}}
  {\emph{1994 -- 1999}}

\item 
  \headerrow
  {\textbf{University of Arizona}}
  {\textbf{Tucson, AZ}}
  \\
  \headerrow
  {\emph{Linguistics/Computer Science}}
  {\emph{2008 -- Present}}

\end{itemize}


\end{document}
