%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{purple}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Leo}{Przybylski}
\title{Resumé}                               % optional, remove / comment the line if not wanted
\address{2450 N. Palo Hacha}{Tucson, AZ}{United States}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{5204401252}                   % optional, remove / comment the line if not wanted
\email{r351574nc3 at gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{https://www.github.com/r351574nc3/}                         % optional, remove / comment the line if not wanted
\extrainfo{https://www.linkedin.com/in/r351574nc3/}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\section{Profile}
\indent A multitool of software engineering. I started software engineering over 25 years 
ago on mainframe systems. Since then, I have developed automation, user interfaces, and 
backends for video games, code generation algorithms, natural language 
processing, financials, research administration, student system administration, 
CMS, digital libraries, scientific programming, machine learning systems, embedded software, 
software deployment, storage systems, SaaS administration, and robotics.
\\\\
\indent I work primarily in software engineering and automation of cloud infrastructure
and orchestration; however, I also enjoy DevOps and Configuration Management. 
I have used the GNU/Linux operating system for over 20 years. I have run it as my 
primary desktop operating system for over 15, and have administered it for over 15 
years as well. I have built and managed firewalls with Linux as well as installed 
it on several devices that are not servers or desktops. I have also built Linux-based 
network appliances (not just firewalls). I can build both RPMs, Debian, and emerge 
packages. 
\\\\
\textbf{Specialties:} Quality Assurance, Configuration Management, Creative Problem 
Solving, Go, java, ruby, perl, python, c/c++, Jenkins, drone, maven, junit, 
testng, mockito, cucumber, docker, puppet, opsworks, aws, spring, sequelize, 
GWT, arduino, ReST, SOAP, SOA, ORM, Liquibase, UML, and Technical Writing.

\textbf{Programming Lanuages:} Node.js, Javascript, Go, Ruby, Java, Scala, Scheme, 
Clojure, Python, Perl, Sed, Awk, Lisp, C/C++, and Bash

\textbf{Cloud Infrastructure:} Google Cloud Platform, AWS, Kubernetes, Docker, Openstack

\textbf{Operating Systems:} Linux, AIX, VAX/Vms, FreeBSD, Solaris, and Mac OS X

\textbf{Frameworks:} Play Framework, Akka, backbone.js, AngularJS, VueJS, GWT, Ruby on Rails, 
SpringBoot, Grails, and DJango

\textbf{Messaging:} Kafka, Storm, RabbitMQ

\textbf{Database platforms:} DynamoDB, MongoDB, Cassandra, CouchDB, Redis, Oracle, and PostgreSQL

\textbf{Build Tools:} drone, Gitlab CI, SBT, Bazel, maven, jenkins, and gradle

\section{Key Competencies}
	16 years experience including n-tier enterprise application development with Java, software 
	documentation with UML, and working with unified/agile processes. 
	\begin{itemize}
	\item Developed software using Ruby, Python, Groovy, and Perl scripting languages.
	\item Strong agile/kanban/iconix development process experience.
	\item Generated source code of XML, SQL, and interpreted scripting languages.
	\item Developed software using SOA and template-driven UI with Oracle and MySQL.
	\item Strong experience with Struts, Spring MVC, RoR, Django, Play Framework, and Grails.
	\item Experience with Rich and Simple domain models with OR/M.
	\item NOSQL database experience with databases like Berkeley DB, BigTable, Redis, and CouchDB.
	\item Enthusiasm and motivation to work with new technologies.
	\item Experienced with Web Components and Polymer/Xtags.
	\item Proven experience with javascript web frameworks like EmberJS and AngularJS.
	\item Proven experience in rich user interfaces with javascript libraries jQuery, Dojo, 
	  prototype, and scriptaculous.
	\item Experience developing Scala on Open Source Software (OSS) projects built on the Play Framework. (Approximately 5 years on 3 projects)
	\item Experience with Scala for Android. 
	\item Aware of tools useful in varying applications, and actively
	  searches for better solutions to improve work output and productivity.
	\item Proven experience in rich user interfaces with AJAX.
	\item Capable of writing/maintaining technical documentation and
	  specifications with LaTeX, UML/ER diagrams, flowcharts, Atlassian Confluence or Microsoft Word.
	\item Strong familiarity with SCM tools RPM, Jenkins, Ant, Ivy, Maven 3, SVN and Git.
	\item Strong familiarity with metadata standards and ontologies
	  including RDF, Dublin Core, FOAF, Microformats, OWL, DAML, and OAI.
	\item Some experience in VB 5.0 from 1997 - 1998.
\end{itemize}
\section{Experience}
%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2018--Current}{Site Reliability Engineer}{Rackspace}{San Antonio, TX}{}{
	%\newline{}%
	\begin{itemize}%
		\item Migrating legacy python 2 application to python 3 (flask) micro-services. 
		\item Mission critical application development and maintenance. 
		\item Developing tools for infrastructure as a service deployment and maintenance. 
		\item Automated deployments to Openshift platform. 
		\item Developed Knative over Openshift proof-of-concept.
	\end{itemize}}
%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2016--2018}{Platform Engineer}{Rackspace}{San Antonio, TX}{}{
\begin{itemize}%
	\item Developed generators with yeoman for application pipelines designed around kubernetes, docker, and jenkins.
	\item Developed extensions to kubernetes (custom resources and controllers) and helm in golang
	\item Developed an event-driven service graph and service discovery architecture that leverages kubernetes
	\item Developed Sonatype Nexus extension that provides insight into charts deployed to nexus and integration with helm
	\item Developed event-driven deployment orchestration third-party-resource for kubernetes
	\item Implemented/Designed reactive Command Request/Query Separation pattern using kafka for event sourcing
	\item Unit testing generators with mocha and chai as promised.
	\item Developed proprietary OAuth2 plugin for Kibana using Bell for OAuth2 using NodeJs.
	\item Developed custom Elastic X-pack realm for proprietary identity management and access control integration.
\end{itemize}}
%\clearpage
%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{2015--2016}{Software Engineer- Hitachi Consulting}{Raytheon Missile Systems}{Tucson, AZ}{}{
	\begin{itemize}
	\item Added Access Control List features to an application built with KnockoutJS, Spring, D3JS, Oracle, and EclipseLink technologies
	\item Developed wizard control elements for KnockoutJS applications
	\item Created an interim Maven repository within SVN until Nexus OSS repository and JFrog Artifactory repository could be evaluated for use.
	\item Developed Jenkins Project plugin for proprietary software development framework project creation.
	\item Developed Yeoman scaffolds for Maven archetypes, Gradle project templates, Docker templates, and NodeJS application.
	\item Developed Maven archetypes for proprietary software development framework projects.
	\item Restructured an entire project for Maven Multi-Module applications with Maven Overlays, Spring Boot, and SVN Externals.
	\item Refactored a large project with static method singleton applications into dependency injected singletons for event and message-driven architecture with Spring Boot, Kafka, and Storm.
	\item Refactored Storm Bolts to run as Spring Boot contexts.
	\item Documented architecture, refactoring changes, howto guides, and developer guides with Docbook.
	\item Created UML class/relationship and sequence diagrams for architecture designs of refactorings.
	\item Created project standards for Jenkins projects including Jacoco configuration, Maven execution configuration, and build pipelines.
	\item Provided documentation and training to developers on the Maven Build Lifecycle, Maven Modules, Maven encryption, and Maven releases.
\end{itemize}}
%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{April 2015--May 2015}{Software Engineer}{American Express}{Phoenix, AZ}{}{
\begin{itemize}
	\item Machine Learning development.
	\item Big Data ETL development.
	\item Developed a Maven archetype for automatically building Maven modules from Talend ETL jobs.
	\item Developed a process for automating unit testing of Talend ETL jobs with JUnit, Jenkins CI, Mockito, and Cobertura code coverage.
	\item Developed a process for automating environment deployments of Talend ETL jobs from a Nexus repository using Maven, Jenkins CI, and capistrano.
	\item Developed a POC for porting a J2EE application built with Spring, EJB, Struts, and DB2 to AngularJS, NodeJS, D3.js, and MongoDB with Siteminder SSO integration.
	\item Developed a POC for replacing ETL using CSV flat files with an HBase (Google Big Table) solution including performance evaluation of transformation speed and resource consumption.
	\item Developed a testable change management refinement for Talend ETL jobs using RPM and Vagrant.
	\item Streamlined execution and configuration management of Talend ETL jobs including a refinement allowing jobs written in different versions of Talend Open Studio to execute together.
	\item Documented development and testing processes using Docbook and Microsoft Sharepoint.
\end{itemize}}

%%%%%% Employer %%%%%%%%%%%%%%%
\cventry{May 2014--October 2014}{SaaS Develooper}{rSmart}{Scottsdale, AZ}{}{
\begin{itemize}
	\item Tools development and features for rSmart Cloud Express platform. These are often tools written in Java or Ruby that work with AWS, Puppet, Hiera, Maven, Jenkins, Tomcat, and MySQL.
	\item Technical advice and guidance directly to the Vice President of Product Development for rSmart Cloud Express on systems and software architecture. 
	\item Work to improve the open source software our product is based on, Kuali Coeus, by adding features and contributing back fixes. 
	\item Development of data migration scripts and tools by developing custom Maven plugins. I also develop custom data migration tools using ReST, Ruby, Spring Framework, and Jersey. 
	\item To improve continuous delivery and adapt software to be more favorable to multitenant applications, I ported a metadata architecture to NoSQL Redis datastore. 
	\item Development of Maven archetypes for KFS, Kuali Coeus, and Kuali Rice platforms to simplify institutions starting new projects. 
	\item Development of integration for Gerrit Code review into Kuali Enterprise Workflow in order to manage real-time modifications to a live application with a workflow.
	\item Software training for Kuali Rice and KRAD.
	\item Preparation of online training tools using Google coursebuilder.
\end{itemize}}

%%%%%% Employer %%%%%%%%%%%%%%%
%\cventry{2011--2011}{Co-op Employee}{MMM Group}{Vancouver B.C.}{}{Assisted Senior Project Engineers and Project Managers design and execute designs of power distribution, lighting and emergency systems in large-scale construction projects.\newline{}
%\begin{itemize}
%	\item Drafted and reviewed project plans using \textit{AutoCad}.
%	\item Designed and developed an award calculator for LEED's mercury-content, 'green'-design award using Excel and Visual Basic.
%	\item Communicated with clients and suppliers on project progress and needs.
%	\item Performed project site inspections.
%\end{itemize}}


\clearpage
% ================== Education ===============%
\section{Education}
\cventry{1994--1999}{AGECS}{Pima County Community College}{Tucson, AZ}{}{
}
\cventry{2008--Present}{Incomplete}{University of Arizona}{Tucson, AZ}{\textit{Linguistics/Computer Science}}{
}  % arguments 3 to 6 can be left empty

%\subsection{Continuing Education and Personal Projects}
%\footnotesize
%*Visit my website for more details, demonstrations and walkthroughs.\newline\newline
% ========= Personal Project =========== %
%\cventry{2017}{Personal Project}{Guitar-Trainer}{}{}{
%	\begin{itemize}
%		\item Unity 5 modelling, animation end engine development.
%		\item Advanced techniques and coding practice.
%		\item Algorithm design.
%	\end{itemize}
%}

%\section{Languages}
%\cvitemwithcomment{Language 1}{Skill level}{Comment}
%\cvitemwithcomment{Language 2}{Skill level}{Comment}
%\cvitemwithcomment{Language 3}{Skill level}{Comment}
%
%\section{Computer skills}
%\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}
%
%\section{Interests}
%\cvitem{hobby 1}{Description}
%\cvitem{hobby 2}{Description}
%\cvitem{hobby 3}{Description}
%
%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}
%
%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}

\section{References}
\emph{Available upon request}
%\begin{cvcolumns}
%\cvcolumn{Kevin Goldstein}{
%	\begin{itemize}
%		\item Title
%		\item Company
%		\item Email:
%		\item Phone:
%	\end{itemize}}
%\cvcolumn{Cesar Alaestante}{
%	\begin{itemize}
%		\item Title
%		\item Company
%		\item Email:
%		\item Phone:
%	\end{itemize}}
%\cvcolumn{Warner Onstine}{
%	\begin{itemize}
%		\item Title
%		\item Company
%		\item Email:
%		\item Phone:
%\end{itemize}}
%\end{cvcolumns}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%\clearpage
%%-----       letter       ---------------------------------------------------------
%% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle
%
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Duis ullamcorper neque sit amet lectus facilisis sed luctus nisl iaculis. Vivamus at neque arcu, sed tempor quam. Curabitur pharetra tincidunt tincidunt. Morbi volutpat feugiat mauris, quis tempor neque vehicula volutpat. Duis tristique justo vel massa fermentum accumsan. Mauris ante elit, feugiat vestibulum tempor eget, eleifend ac ipsum. Donec scelerisque lobortis ipsum eu vestibulum. Pellentesque vel massa at felis accumsan rhoncus.
%
%Suspendisse commodo, massa eu congue tincidunt, elit mauris pellentesque orci, cursus tempor odio nisl euismod augue. Aliquam adipiscing nibh ut odio sodales et pulvinar tortor laoreet. Mauris a accumsan ligula. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Suspendisse vulputate sem vehicula ipsum varius nec tempus dui dapibus. Phasellus et est urna, ut auctor erat. Sed tincidunt odio id odio aliquam mattis. Donec sapien nulla, feugiat eget adipiscing sit amet, lacinia ut dolor. Phasellus tincidunt, leo a fringilla consectetur, felis diam aliquam urna, vitae aliquet lectus orci nec velit. Vivamus dapibus varius blandit.
%
%Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.
%
%Albert Einstein discovered that $e=mc^2$ in 1905.
%
%\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]
%
%\makeletterclosing
%
%%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
